Delone lattice studies in \CIII, the space of three complex variables

### 2023-03-06 C3/C3.tex
FInish cover letter to mois for Measuing Lattices C3, start on adding section on graphics
C3.tex -- updating

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

	~\citeasnoun{andrews2019b} chose to 
	represent the scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. T
	hey also consider the representation of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).
	Also consider that each complex term uses all 
	four 3-space vectors; for example, $c_1$ is ($b \cdot c$, $a \cdot d$)

	~\citeasnoun{andrews2019b} considered the matrix representations 
	of the reflections in \CIII{} (and in \SVI{}). 
	This paper will describe the boundary transformations 
	at the edges of the fundamental	unit of \CIII{}. 
	In \SVI{}, the fundamental unit is the all negative orthant, 
	which contains only and	all of the reduced cells. 
	In \SVI{} and \CIII{}, 
	the boundaries are found where any scalar 
	(or correspondingly the real or imaginary part) 
	is equal to zero. The rationale for this work was 
	that it might lend insights into the topology of
	the space of lattices.

@@

	If considered in \CIII, Delone's alternate transformation 
	for the \si{} boundary would
	exchange the real of \cii{} 
	with the imaginary part of \ciii{}. That is the fourth
	matrix in the list for \si{}. 
	The other two transformations for \si{} can 
	be generated from the two we have 
	just displayed by the "exchange operation"~\cite{andrews2019b} 
	applied to the second and third \CIII{} elements. Delone 
	did not describe the latter two transformation, 
	perhaps because even a single transformation 
	was adequate to implement reduction. He already listed two.

@@

	The considerable regularity 
	of the transformation matrices (above) highlights one
	of the important aspects of Selling reduction 
	as used by~\citeasnoun{Delaunay1932}
	when compared to Niggli reduction~\cite{Niggli1928}. 
	Where all the 	boundaries of the fundamental orthant 
	\SVI{} (and also \CIII{}) are basically the same 
	(and indeed are related by reflections), 
	the boundaries formed in Niggli reduction are of multiple types, 
	and the fundamental unit of the space representing 
	Niggli reduced cells (\GVI{}, see~\citeasnoun{Andrews2014}) is non-convex.

	The matrices display one of the properties of \CIII{} 
	that make it a useful conceptual representation. 
	For the scalar being transformed, it and its 
	opposite scalar create a unique row in each matrix. 
	Those rows contain
	only the minus operator and zeros, 
	highlighting the unique relationship of that pair of scalars.

	Several aspects of \CIII{} are obvious from inspecting the matrices above. 
	First, we see that each boundary has four possible 
	transformations that can be applied. 
	Because the each of the transformations at boundaries are self-inverse, 
	they are the same transformations that would 
	be used in the process of cell (lattice) reduction. 
	~\citeasnoun{Delaunay1932} and~\citeasnoun{Delone1975} give 
	only two choices. Presumably for simplicity they did not list
	the transformations that used the "exchange" operator 
	(see~\cite{andrews2019b}).

>>>>

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

	~\citeasnoun{andrews2019b} chose to 
	represent the Selling scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. 
	They also consider the representation of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Selling scalars, 
	a vector is defined as \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).
	Additionally, each complex term uses all 
	four 3-space vectors; for example, $c_1$ is ($b \cdot c$, $a \cdot d$).

	~\citeasnoun{andrews2019b} considered the matrix representations 
	of the reflections in \CIII{} (and in \SVI{}). 
	This paper describes the boundary transformations 
	at the edges of the fundamental	unit of \CIII{}. 
	In \SVI{}, the fundamental unit is the all negative orthant, 
	which contains only and	all of the reduced cells. 
	In \SVI{} and \CIII{}, 
	the boundaries located where any \SVI{} scalar 
	(or correspondingly in\CIII{}, the real or imaginary part) 
	equals to zero. The rationale for this work was 
	that it might lend insights into the topology of
	the space of lattices.

@@

	Considered in \CIII, Delone's alternate transformation 
	for the \si{} boundary would
	exchange the real of \cii{} 
	with the imaginary part of \ciii{}. That is the fourth
	matrix in the list for \si{}. 
	The other two transformations for \si{} can 
	be generated from the two we have 
	just displayed by the "exchange operation"~\cite{andrews2019b} 
	applied to the second and third \CIII{} coordinates. Delone 
	did not describe the latter two transformation, 
	perhaps because even a single transformation 
	was adequate to implement reduction. He already listed two.

	\section{Graphical display of projections}

%	Although printing the image of a 6-dimensional object
%	is impossible, there is some utility to creating the
%	2-dimensional projections of \CIII{} onto the three
%	coordinates.

@@

The transformation matrices shown above demonstrate the 
considerable regularity of Selling reduction, as used by 
Delaunay (1932), in comparison to Niggli 
reduction \cite{Niggli1928}. While all the boundaries of the non-positive 
orthant of \SVI{} are essentially the same (and 
related by reflections), the boundaries formed in 
Niggli reduction are of multiple types, and the fundamental unit 
of the space representing Niggli reduced cells (\GVI{}, see \citeasnoun{Andrews2014}) is non-convex.

The matrices also display one of the unique properties of \CIII{}, 
which makes it a useful conceptual representation. 
For the scalar being transformed, it and its opposite scalar
create a unique row in each transformation matrix. These rows contain only
the minus operator and zeros, highlighting the 
unique relationship of that pair of scalars.

Several aspects of \CIII{} are evident from inspecting the matrices. 
First, each boundary has four possible 
transformations that can be applied. Since each of 
the transformations at boundaries are self-inverse, they are the 
same transformations that would be used in the process of 
cell (lattice) reduction. \citeasnoun{Delaunay1932} and \citeasnoun{Delone1975} give only two choices, presumably for simplicity, 
omitting transformations that use the "exchange" operator 
(see \citeasnoun{andrews2019b}).
